%!TEX root = ../documentation.tex

\chapter{Application requirement analysis}\label{cha:requirement}

In order to evaluate if there is a need for a generalized shell application, it is important to first understand what the requirements for such an application are.
To get the needed insights a requirement analysis is conducted via literature research and the expert interviews.
This chapter focuses on outlining requirements and comparing them against each other.

The found requirements can be divided into categories.
These are explained in section \ref{cha:requirement_categories}.
After that, an overview of all requirements is provided in the section \ref{cha:requirements_overview}.
This includes an explanation on how the requirements were compared against each other in terms of importance, and an overview, seen in Table \ref{tbl:overview_requirements}, which contains all found requirements.
Following that are multiple sections which describe the requirements in detail (section \ref{cha:requirement_detail_integration}, \ref{cha:requirement_detail_performance}, \ref{cha:requirement_detail_state}, \ref{cha:requirement_detail_style} and \ref{cha:requirement_detail_developer}).
Lastly, a conclusion for this chapter is drawn in section \ref{cha:requirements_conclusion}.



\input{content/Requirements/Categories.tex}

\section{Requirement analysis result overview}\label{cha:requirements_overview}

The analysis led to many requirements.
To better outline the importance of each requirement, they need to be scored in some way.
In order to achieve this, the process of the pairwise comparison technique is used.
This technique determines the relative importance by comparing requirements against each other and thus, obtaining a score for all requirements \cite[p.~573]{Achimugu.2014}.

The technique was modified in order to use it for the requirement analysis.
Instead of weighting the requirements, the expert statements are weighted based on the questions.
In the expert interviews, the questions four, five and six are used to gain insights into requirements and their approaches (see \ref{cha:appendix_expertinterview_questions}).
Each of the questions is assigned with a different weight.

\begin{itemize}
    \item Question four, \textit{What are requirements for the named shell application scenario which you had from a customer?}: They can be an any importance and thus, receive a score of 1
    \item Question five, \textit{Can you name any requirements which are needed for all shell application scenarios?}: These are the most important requirements in context of this thesis and thus, receive a score of 3
    \item Question six, \textit{What are the most difficult requirements to achieve and why?}: A general goal of architecture is to reduce the complexity of a project \cite[p.~98]{AlSharif.2004} and therefore, these requirements receive a score of 2
\end{itemize}

By introducing the score the focus can be shifted towards the relevant requirements.
Therefore, the requirements with a score of 5 or higher are considered relevant.
The reason is, that a low score makes it less likely that a requirement is actually needed.
It is important to note, that not all requirements can be part of a generalized shell application.
Hence, low scoring requirements are considered but they are a optional feature of the generalized shell application.


The requirements analysis was not only conducted via the expert interview, but also through a literature research.
Requirements found in the literature research receive a score of 1, because the context is not the same as in the expert interviews and therefore, comparability is not guaranteed \cite[p.~35]{AlexanderBognerBeateLittigWolfgangMenz.2009}.
On the other hand, requirements mentioned in literature should be considered as well to ensure a broad view.
Therefore, a score equivalent of question four in the interview is suitable.

After collecting the weights for each requirement, the weights are added up and resulting in the score.
In case of a score tie, the respective requirements are considered equally relevant.
Also, requirements are not only ordered by their score, but also by their respective category.
The categories are explained in the next section \ref{cha:requirement_categories}.

An overview of the requirement analysis result is shown in Table \ref{tbl:overview_requirements}.
In addition to this Table, there are two more tables in the appendix \ref{cha:appendix_requirements_overview}.
The first (\ref{tbl:adx_requirements_scores}) shows the score of each requirement and the second (\ref{tbl:adx_requirements_references}) shows which reference mentioned the requirement, considers it as difficult and as critical.
Further detail for the requirements will be provided in the following sections from  \ref{cha:requirement_detail_integration} to \ref{cha:requirement_detail_developer}.

\input{content/Requirements/OverviewTable.tex}
\input{content/Requirements/Integration.tex}
\input{content/Requirements/Performance.tex}
\input{content/Requirements/State.tex}
\input{content/Requirements/Style.tex}
\input{content/Requirements/Developer.tex}
\input{content/Requirements/Conclusion.tex}

