%!TEX root = ../documentation.tex

%
% vorher in Konsole folgendes aufrufen:
%	makeglossaries makeglossaries documentation.acn && makeglossaries documentation.glo
%

%
% Glossareintraege --> referenz, name, beschreibung
% Aufruf mit \gls{...}
%
\newglossaryentry{Glossareintrag}{name={Glossareintrag},plural={Glossareinträge},description={Ein Glossar beschreibt verschiedenste Dinge in kurzen Worten}}

\newglossaryentry{Commodity-Hardware}{name={Commodity-Hardware},description={\flqq Computer hardware that is affordable and easy to obtain. Typically it is a low-performance system that is IBM PC-compatible and is capable of running Microsoft Windows, Linux, or MS-DOS without requiring any special devices or equipment.\frqq\footcite{Beal.2015}}}

\newglossaryentry{Git}{name={Git},plural={Git},description={Git ist ein kostenloses System zur Versionskontrolle für kleine wie auch sehr große Projekte. ({\url{http://git-scm.com/}})}}

\newglossaryentry{NetBeans}{name={NetBeans},plural={NetBeans},description={The Smarter and Faster Way to Code Quickly and easily develop desktop, mobile and web applications with Java, HTML5, PHP, C/C++ and more. NetBeans IDE is FREE, open source, and has a worldwide community of users and developers. ({\url{https://netbeans.org}})}}

\newglossaryentry{Maven}{name={Maven},plural={Maven},description={Apache Maven is a software project management and comprehension tool. Based on the concept of a project object model (POM), Maven can manage a project’s build, reporting and documentation from a central piece of information. \\ ({\url{http://maven.apache.org/}})}}

\newglossaryentry{Nagios}{name={Nagios},plural={Nagios},description={Nagios Is The Industry Standard In IT Infrastructure Monitoring. Achieve instant awareness of IT infrastructure problems, so downtime doesn't adversely affect your business. Nagios offers complete monitoring and alerting for servers, switches, applications, and services. \\ ({\url{https://www.nagios.org}})}}

\newglossaryentry{Zabbix}{name={Zabbix},plural={Zabbix},description={Zabbix is the ultimate enterprise-level software designed for real-time monitoring of millions of metrics collected from tens of thousands of servers, virtual machines and network devices. Zabbix is Open Source and comes at no cost. \\ ({\url{http://www.zabbix.com}})}}

\newglossaryentry{Bootstrapping}{name={Bootstrapping},description={\flqq The computer term bootstrap began as a metaphor in the 1950s. In computers, pressing a bootstrap button caused a hardwired program to read a bootstrap program from an input unit. The computer would then execute the bootstrap program, which caused it to read more program instructions. It became a self-sustaining process that proceeded without external help from manually entered instructions. As a computing term, bootstrap has been used since at least 1953.\frqq\footcite[S. 1273]{Buchholz.1953}}}

\newglossaryentry{Generic}{name={Generic},plural={Generics},description={Ein Interface oder eine Klasse kann mit einem oder mehreren Parametern, den sog. Generics, definiert werden, welche zusätzliche Typangaben enthalten. Diese werden in spitzen Klammern notiert. Generics führen implizit einen Typumwandlung durch, welcher ohne Generics explizit erfolgen müsste\footcite[Vgl.][S. 4 f.]{Naftalin.2006}}}

\newglossaryentry{Plugin}{name={Plugin},plural={Plugins},description={\flqq Zusatzprogramm, welches über eine vordefinierte Schnittstelle in ein Basisprogramm eingebunden wird und dessen Funktionsumfang erweitert. [...] [Stammen] oftmals von anderen Herstellern als das Basisprogramm. [...] Plug-ins sind oft aus eigenständigen Programmen entstanden und können deshalb [...] i.d.R. auch ohne das Basisprogramm verwendet werden\frqq\footcite[]{Lackes.2015}}}